\documentclass[11 pt]{article} 
\usepackage[left=2cm, top=2cm, right=2cm, bottom=2.5cm, footskip=.5cm]{geometry}
\usepackage{url}
\usepackage{enumitem}

\author{Natalia Zuniga-Garcia}
\title{Peer Review 3. Shout-Outs}
\date{December 12, 2017}

\begin{document}

\maketitle

The last peer-review consist of assessing the contributions of other students to my learning process during the semester. In this document I shout-out those folks who made the most significant contributions. 

\section{Mauricio Garcia-Tec}

I am very grateful with Mauricio for his help since the beginning of the course. His in-class presentation helped me to better understand the exercises. He was always suggesting new methods and better ways to present the results. For instance, he suggested using R-Markdown to present our solutions. I found this very useful to explain wider the code and, since then, I have been using it widely for this course and for other assignments. Mauricio was also very helpful when I was having troubles in some parts of the exercises, and he attended all my questions even during off-class time. 

In addition, Mauricio is my teammate for the term project of the course. His coding skills and statistical background is very impressive. It has been very nice working with him. He is always making sure I understand the methods and he is always trying to teach me his coding skills. I have learned a lot from Mauricio this semester.


\section{Ciara Nugent}

I am also very grateful with Ciara. Her in-class presentations were very useful. In specific, I like her presentations involving some mathematical proofs. Her explanations were very easy to follow.

\section{Bowen Hua}
I also wanted to thank Bowen. He made a lot of contributions to the class. He was always willing to present his work and to explain us his solutions. For instance, his ADMM explanation in class was very helpful.  In addition, his code was always very clean and clear. 

\section{Amin Anvari}
Amin contributed a lot to class as well. I like the way he explained the exercises on his GitHub page. I specifically like Exercises 5, which he explained in class. The way he explained the comparison between the Lasso and the Ridge regression before applying the solution helped a lot. I also found very interesting his short-presentation about Uber drivers. Thanks Amin!

\section{Yanxin Li}
I had the opportunity to review Yanxin's work for the last two Peer Reviews. I found some of her solutions very interesting and I specifically like the way she presented her code. I also used some of her code style after reviewing her. I wanted to thank Yanxin because I leaned a lot from her as well.

\section{James Scott}
Finally, I wanted to thank James Scott. I leaned an incredible amount of things from his class. I specifically like that the course was mainly focused on the application of the methods and not only the theory, which made us understand even more. Also, he encouraged a lot the peer-collaboration which made possible learning a broad amount of skills from each others.

\end{document}